---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center",
  fig.width = 6,
  fig.height = 4,
  dpi = 300,
  out.width = "90%",
  auto_pdf = TRUE,
  message = FALSE,
  warning = FALSE
)
```

# dorem

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3757085.svg)](https://doi.org/10.5281/zenodo.3757085)
<!-- badges: end -->

The goal of `dorem` is to provide easy-to-use dose-response models utilized in sport science. This package is currently in active development phases. 

## Installation

You can install the development version from [GitHub](https://github.com/mladenjovanovic/dorem) with:

``` r
# install.packages("devtools")
devtools::install_github("mladenjovanovic/dorem")

require(dorem)
```

## Example

To provide very simplistic example of `dorem`, I will use example data provided in [supplementary material](https://journals.physiology.org/doi/full/10.1152/advan.00078.2011m) of Clarke & Skiba, 2013 [paper](https://journals.physiology.org/doi/full/10.1152/advan.00078.2011?), freely available on the publisher website. Data set contains cycling training load (i.e. dose) measured using the BikeScore metric (in AU) over 165 days, with occasional training response measured using 5-min Power Test (in Watts). *Banister* model (explained in aforementioned paper) is applied to understand relationship between *training dose* (i.e., BikeScore metric) and *training response* (i.e., 5-min Power Test): 

```{r fig.width=6, fig.height=6}
require(dorem)
require(tidyverse)
require(cowplot)

data("bike_score")

banister_model <- dorem(
   Test_5min_Power ~ BikeScore,
   bike_score,
   method = "banister"
)

# Get model predictions
bike_score$pred <- predict(banister_model, bike_score)$.pred

# Plot
dose <- ggplot(bike_score, aes(x = Day, y = BikeScore)) +
  theme_cowplot(10) +
  geom_bar(stat = "identity") +
  xlab(NULL)

response <- ggplot(bike_score, aes(x = Day, y = pred)) +
   theme_cowplot(10) +
   geom_line() +
   geom_point(aes(y = Test_5min_Power), color = "red") +
   ylab("Test 5min Power")

cowplot::plot_grid(dose, response, ncol = 1)
```

This package is in ongoing development phase and more examples will follow...

## References

Clarke DC, Skiba PF. 2013. Rationale and resources for teaching the mathematical modeling of athletic training and performance. Advances in Physiology Education 37:134–152. DOI: 10.1152/advan.00078.2011.
